Happiness in America: A Comprehensive Analysis of the Effects of Demographic Factors

### 2023-03-16 outputs/paper/Happiness in America: A Comprehensive Analysis of the Effects of Demographic Factors.qmd
rename employee status to employee type

fig1 <- ggplot(happiness_data, aes(x = Year, y = People, fill = Happy_level)) +
  geom_line(aes(group = Happy_level, color = Happy_level), size = 1.2) +
  scale_fill_manual(values = happy_colors) +
  scale_color_manual(values = happy_colors) +
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       color = "Happy level")
fig1 <- fig1  +
  draw_label("Trends in happiness levels for different genders from 1972 to 2021", 
             fontface = "bold", 
             size = 12,
             x = 0.5,
             y = 1.05)
fig1
```

@@

fig2 <- fig2  +
  draw_label("Trends in happiness levels for different genders from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
fig2
```

@@

fig3 <- fig3  +
  draw_label("Trends in happiness levels for different races from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
fig3

@@

fig4 <- fig4  +
  draw_label("Trends in happiness levels for different degrees from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
fig4
```

@@

fig5 <- fig5  +
  draw_label("Trends in happiness levels for different emoloyee status from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
fig5
```

@@

fig6 <- fig6  +
  draw_label("Trends in happiness levels for different emoloyee status from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
fig6
```

>>>>

fig1 <- ggplot(happiness_data, aes(x = Year, y = People, fill = Happy_level)) +
  geom_line(aes(group = Happy_level, color = Happy_level), size = 1.2) +
  scale_fill_manual(values = happy_colors) +
  scale_color_manual(values = happy_colors) +
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       color = "Happy level")
fig1 <- fig1  +
  draw_label("Trends in happiness levels for different genders from 1972 to 2021", 
             fontface = "bold", 
             size = 12,
             x = 0.5,
             y = 1.05)
```

@@

fig2 <- fig2  +
  draw_label("Trends in happiness levels for different genders from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
```

@@

fig3 <- fig3  +
  draw_label("Trends in happiness levels for different races from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
```

@@

fig4 <- fig4  +
  draw_label("Trends in happiness levels for different degrees from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
```

@@

fig5 <- fig5  +
  draw_label("Trends in happiness levels for different emoloyee status from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
```

@@

fig6 <- fig6  +
  draw_label("Trends in happiness levels for different emoloyee status from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
```
